---
title: "_MSExample_: A simple example package for mass spectrometry"
author: "Kylie Ariel Bemis"
date: "May 1, 2019"
output:
  BiocStyle::html_document:
  toc: true
vignette: >
  %\VignetteIndexEntry{MSExample: A simple example package for mass spectrometry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results='asis'}
BiocStyle::markdown()
```

# Introduction 

*MSExample* is a simple example package for mass spectrometry (MS).

It implements some basic classes and methods for working with raw MS data, including:

- plotting spectra

- smoothing spectra

- baseline correction

- peak detection

- peak binning

It is not intended for actual use, but rather as an example of Bioconductor package development for the Advanced R session of the May Institute Computation and Statistics for mass spectrometry and proteomics short course at Northeastern University

# Simulating spectra

We can use the `simSpectra` to simulate a mass spectrum.

```{r sim}
library(MSExample)

set.seed(2019)
s1 <- simSpectra(baseline=4)
```

Mass spectra are represented as `MassSpectrum` objects.

```{r spectrum}
s1
```

# Plotting spectra

Use `plot()` to plot a `MassSpectrum`.

```{r plot, fig.height=4, fig.width=8}
plot(s1)
```

# Spectral processing


Several processing options are provided.


## Smoothing

Use `smoothNoise()` to smooth a `MassSpectrum`.

```{r smooth, fig.height=4, fig.width=8}
s2 <- smoothNoise(s1)

plot(s2)
```

## Baseline correction

Use `removeBaseline()` to baseline correct a `MassSpectrum`.

```{r baseline, fig.height=4, fig.width=8}
s3 <- removeBaseline(s2)

plot(s3)
```

## Peak detection

Use `findPeaks()` to detect peaks in a `MassSpectrum`.

```{r peaks, fig.height=4, fig.width=8}
s4 <- findPeaks(s3)

plot(s4)
```

## Bin peaks


Use `binPeaks()` to bin a `MassSpectrum` to detected peaks.

```{r bin, fig.height=4, fig.width=8}
s5 <- binPeaks(s4)

plot(s5)
```

# Session information

```{r}
sessionInfo()
```

